---
title: "Project 1 - Alon Goodman & Ran Hassid"
output:
  html_document:
    df_print: paged
---

# Q1 - Snakes & Ladders #

## The Board Game ##

```{r}
Start_of_Ladder <- c(2,7,8,15,21,28,36,51,71,78,87)
End_of_Ladder <- c(38,14,31,26,42,84,44,66,91,98,94)
Start_of_Snake <- c(16,46,49,62,64,74,89,92,99)
End_of_Snake <- c(6,25,11,19,60,53,68,88,80)
```



## Auxiliary Function - Sum of Digit ##

```{r}
digitsum <- function(n) {
  while(n>=10){
  n <-n %% 10 + floor(n / 10)
  }
  return(n)
  }
```

## One game Function ##

1. Rolling the dice.

2. Check if we crossed the 100 and go back.

3. Check if the final sum of digits is equal to value of the dice.

4. Handle the snakes and ladders.

```{r}
Sanke_and_Ladder <- function(Start_of_Ladder,End_of_Ladder,Start_of_Snake,End_of_Snake){
  Snake <- data.frame(Start_of_Snake,End_of_Snake) # A table of where the snake start $ end
  Ladder <- data.frame(Start_of_Ladder,End_of_Ladder) # A table of where the ladder start $ end
  number_of_rolls <- 0 
  counter <- 1 # The location of the player
  while(counter < 100){
    dice_roll <- sample(1:6,1) # Rolling the dice
    number_of_rolls <-  number_of_rolls + 1
    counter <- counter + dice_roll
    if (counter > 100){ # Check if we crossed the 100 and go back
      dif <- counter - 100
      counter <- 100 - dif
      }
    if (digitsum(counter) == dice_roll){ # Check if the final sum of digits is equal to value of the dice.
      counter <- floor(counter/2)
      }
    if  (any(counter==Snake$Start_of_Snake)==T){ # Handle the snakes
      counter <- Snake$End_of_Snake[Snake$Start_of_Snake == counter]}
    if  (any(counter==Ladder$Start_of_Ladder)==T){ # Handle the ladders
      counter <- Ladder$End_of_Ladder[Ladder$Start_of_Ladder == counter]}
    }
  return (number_of_rolls)
}
```

## The Simulation ##
```{r}
Sanke_and_Ladder_sim <- replicate(5000,Sanke_and_Ladder(Start_of_Ladder,End_of_Ladder,Start_of_Snake,End_of_Snake))
```

### The Expected value ###
```{r}
mu <- mean(Sanke_and_Ladder_sim)
mu
```

### Confidance Interval of 95% - CLT ###
```{r}
sd <- sqrt(var(Sanke_and_Ladder_sim)/5000)
up <- mu + qnorm(0.975)*sd
low <- mu - qnorm(0.975)*sd
CI <- c(low,up)
CI
```

# Q2 - X & O #

```{r}
#install.packages("matricks")
#install.packages("lattice")
library(matricks)
library(tidyverse)
```

```{r}
check_if_win <- function(board,turn){
  # input: board size and turn. output: True if the player won in this turn, False if not.
  row_size <- sqrt(length(board))
  board_matrix <- matrix(data = board,nrow = row_size,ncol = row_size)
  any(c(apply(X = board_matrix==turn,FUN = all,MARGIN = 1), apply(X = board_matrix==turn,FUN = all,MARGIN = 2), all(diag(board_matrix) == turn), all(antidiag(board_matrix) == turn)))
}
```

```{r}
game <- function(size) {
  # input: board size, output: a X/O game (possible results: Player 1 win = 1,Player 2 win = 2, Tie =3)
  game_board <- numeric(size*size)
  turn <- 1
  game_result <- 0
  
  
  while (game_result==0) {
    # continue untill there is a game result (1,2,3)
    game_board[sample(x = which(game_board==0),size = 1)] <- turn # sample the next place on the board from the available places
    if (check_if_win(game_board,turn)) {
      game_result <- turn
    } # if the player won - determine the game result
    
    turn <- ifelse(test = turn==1, yes = 2, no = 1) # change the turn for next loop
    
    if (sum(game_board==0)==1) {
      game_board[which(game_board==0)] <- 1
      game_result <- ifelse(test = check_if_win(game_board,turn), yes = 1, no = 3)
    } # if its the last turn in the game, check if player 1 win (game result: 1) or its a tie (game result: 3)
  }
  game_result
}
```

```{r}
board_sizes <- c(3:15,25,50)
final_results <- matrix(data = numeric(15*3),nrow = 15,ncol = 3,dimnames = list(board_sizes,c("1 win","2 win","tie")))

# simulate games for n=5000, board sizes as required and caculte the probs for each option (winners and tie)
for (i in 1:15) {
  temp_result <- replicate(n = 5000,expr = game(board_sizes[i]))
  final_results[i,1] <- mean(temp_result==1)
  final_results[i,2] <- mean(temp_result==2)
  final_results[i,3] <- mean(temp_result==3)
  print(i)
}
```

```{r}
# prepare the data for heatmap
X<-cbind(arrayInd(1:(nrow(final_results)*ncol(final_results)),.dim=dim(final_results)),c(as.matrix(final_results)))
X<-setNames(as.data.frame(X),c("board_size","winner","probs"))
X<-transform(X,fill=(probs))
```

```{r}
# heatmap
ggplot(X,aes(x=board_size,y=winner,show.legend = FALSE)) +
  geom_tile(aes(fill=fill)) +
  scale_fill_gradient(low = "deepskyblue", high = "red", limits = c(0, 1), breaks = seq(0,1,.1), guide = guide_legend("probs")) +
  geom_text(aes(label=round(probs,1))) +
  ggtitle("Probs of X/O winner as a function of board sizes simulation") +
  scale_x_discrete(name ="Board Size", limits=as.character(board_sizes)) +
  scale_y_discrete(name ="Winner", limits=c("Player 1","Player 2","Tie"))
```

# Q3 - Dogcatia #

## 3.1 ##

### a,b,c ###

```{r}
dogcatia_10<-function()
{
  # arrival times of dogs
  dogs.arrive.time<-rexp(1,3)
  
  while(dogs.arrive.time[length(dogs.arrive.time)]<720)
  {
    dogs.arrive.time<-c(dogs.arrive.time,dogs.arrive.time[length(dogs.arrive.time)]+rexp(1,3))
  }
  
  # arrival times of cats
  cats.arrive.time<-rexp(1,1.5)
  while(cats.arrive.time[length(cats.arrive.time)]<720)
  {
    cats.arrive.time<-c(cats.arrive.time,cats.arrive.time[length(cats.arrive.time)]+rexp(1,1.5))
  }
  
  #service time's of dogs
  dogs.serve.time<-rexp(length(dogs.arrive.time),3)
  
  #service time's of cats
  cats.serve.time<-rexp(length(cats.arrive.time),5)
  
  
  # initialization
  work.clock<-0   # marks the current time
  serve_start_time<-0   # a time when the next animal serve will begin
  profit<-0   # the company profit
  waited<-c()   # a vector of the queuing aninals
  dogs_out<-c()   # a vector for the served dogs
  cats_out<-c()   # a vector for the served cats
  dog.served.counter<-0   #number of dogs have served 
  cat.served.counter<-0   #number of dogs have served
  dog.not.served.counter<-0   # number of dogs have rejected
  cat.not.served.counter<-0   # number of cats have rejected
  dogs.times<-dogs.arrive.time  # arrival times vector of dogs
  cats.times<-cats.arrive.time   # arrival times vector of cats
  num_waited<-c(0)   # a vector of the number of queuing aninals at all time intervals
  num_times<-c(0)   # a vector of the start time of the intervals 
  # as long as 12 hours have not passed
  while(work.clock<=720)   
  {
    #"x" is the next animal that arrived
    x<-min(dogs.times[1],cats.times[1])
    # check if "x" is a dog or a cat
    if(x==dogs.times[1])
    {
      type_x<-"dog" 
    }else
    {
      type_x<-"cat"
    }
    # if the shop is open
    if(work.clock<x)
    {
      # if there is no animal that in the queue
      if(length(waited)==0)
      {
        # so "x" can enter to the shop
        serve_start_time<-x
        # calculate the time that "x" will finish the service
        if(type_x=="dog")
        {
          work.clock<-serve_start_time+dogs.serve.time[which(dogs.arrive.time==x)]
        }
        if(type_x=="cat")
        {
          work.clock<-serve_start_time+cats.serve.time[which(cats.arrive.time==x)]
        }
        # check if "x" will finish the srvice before the shop will close
        if(work.clock<=720)
        {
          if(type_x=="dog")
          {
            dog.served.counter<-dog.served.counter+1
            profit<-profit+1
            dogs_out<-c(dogs_out,x)
            dogs.times<-dogs.times[-1]
          }
          if(type_x=="cat")
          {
            cat.served.counter<-cat.served.counter+1
            profit<-profit+3
            cats_out<-c(cats_out,x)
            cats.times<-cats.times[-1]
          }
        }
      }
      # if the shop is open now, but there are animals that waiting in the queue before "x"
      if(length(waited)>0)
      {
        # the first animals in the queue will enter to get a service
        serve_start_time<-work.clock
        num_times<-c(num_times, serve_start_time)
        # check if the first animal in the queue is a dog or a cat
        if(any(dogs_out==waited[1]))
        {
          first_waited_type<-"dog"
        }
        if(any(cats_out==waited[1]))
        {
          first_waited_type<-"cat"
        }
        # calculate the time that the first animal in the queue will finish the service
        if(first_waited_type=="dog")
        {
          work.clock<-serve_start_time+dogs.serve.time[which(dogs.arrive.time==waited[1])]
        }
        if(first_waited_type=="cat")
        {
          work.clock<-serve_start_time+cats.serve.time[which(cats.arrive.time==waited[1])]
        }
        # check if he will finish before the shop will close
        if(work.clock<=720)
        {
          if(first_waited_type=="dog")
          {
            dog.served.counter<-dog.served.counter+1
            profit<-profit+1
          }
          if(first_waited_type=="cat")
          {
            cat.served.counter<-cat.served.counter+1
            profit<-profit+3
          }
          #remove the customer from the line
          waited<-waited[-1]
          num_waited<-c(num_waited, length(waited))
        }
      }
      # if the shop is not open  
    }else
    {
      #if "x" is a cat
      if(type_x=="cat")
      {
        # and there is nobody that waiting in queue ,
        #"x" will enter the queue
        if(length(waited)==0)
        {
          waited<-c(waited,x)
          num_waited<-c(num_waited, length(waited))
          num_times<-c(num_times, waited[length(waited)])
          #if there are customers that waiting in the queue,
          #"x" will be rejected
        }else
        {
          cat.not.served.counter<-cat.not.served.counter+1
        }
        cats_out<-c(cats_out,x)
        cats.times<-cats.times[-1]
      }
      #if "x" is a dog
      if(type_x=="dog")
      {
        #and there is a place for "x" in the queue, 
        #"x" will enter the queue
        if(length(waited)<10)
        {
          waited<-c(waited,x)
          num_waited<-c(num_waited, length(waited))
          num_times<-c(num_times, waited[length(waited)])
          #if there is no place for "x" in the queue
          #"x" will be rejected
        }else
        {
          dog.not.served.counter<-dog.not.served.counter+1
          profit<-profit-0.1
        }
        dogs_out<-c(dogs_out,x)
        dogs.times<-dogs.times[-1]
      }
    }
  }
  # calculate the average number of animals in the queue
  num_times_help<-(num_times)-(c(0,num_times[-length(num_times)]))
  final_num_times<-num_times_help[-1]
  if(length(num_waited)>length(final_num_times))
  {
    if(num_waited[length(num_waited)]==0)
    {
      num_waited<-num_waited[-length(num_waited)]
    }
  }
  mean_queue<-(sum(num_waited * final_num_times))/720
  return(list("dogs_served"=dog.served.counter, "dogs_reject"=dog.not.served.counter, "cats_served"=cat.served.counter, "cats_reject"=cat.not.served.counter, "profit"=profit, "mean_queue"=mean_queue))
}
```

```{r}
results_1<-replicate(100,dogcatia_10())

dogs_served_estimator_10 <- mean(as.numeric(results_1[1,]))
dogs_reject_estimator_10<-mean(as.numeric(results_1[2,]))
cats_served_estimator_10<-mean(as.numeric(results_1[3,]))
cats_reject_estimator_10<-mean(as.numeric(results_1[4,]))
profit_estimator_10<-mean(as.numeric(results_1[5,]))
mean_queue_estimator_10<-mean(as.numeric(results_1[6,])) 
```

```{r}
cat(paste("The dogs served estimator is",dogs_served_estimator_10,
        "The dogs reject estimator is",dogs_reject_estimator_10,
        "The cats served estimator is",cats_served_estimator_10,
        "The cats reject estimator is",cats_reject_estimator_10,
        "The profit estimator is",profit_estimator_10,
        "The mean queue estimator is",mean_queue_estimator_10,sep = "\n"))
```

## 3.2 ##

### a ###

```{r}
dogcatia_20<-function()
{
  # arrival times of dogs
  dogs.arrive.time<-rexp(1,3)
  
  while(dogs.arrive.time[length(dogs.arrive.time)]<720)
  {
    dogs.arrive.time<-c(dogs.arrive.time,dogs.arrive.time[length(dogs.arrive.time)]+rexp(1,3))
  }
  
  # arrival times of cats
  cats.arrive.time<-rexp(1,1.5)
  while(cats.arrive.time[length(cats.arrive.time)]<720)
  {
    cats.arrive.time<-c(cats.arrive.time,cats.arrive.time[length(cats.arrive.time)]+rexp(1,1.5))
  }
  
  #service time's of dogs
  dogs.serve.time<-rexp(length(dogs.arrive.time),3)
  
  #service time's of cats
  cats.serve.time<-rexp(length(cats.arrive.time),5)
  
  
  # initialization
  work.clock<-0   # marks the current time
  serve_start_time<-0   # a time when the next animal serve will begin
  profit<-0   # the company profit
  waited<-c()   # a vector of the queuing aninals
  dogs_out<-c()   # a vector for the served dogs
  cats_out<-c()   # a vector for the served cats
  dog.served.counter<-0   #number of dogs have served 
  cat.served.counter<-0   #number of dogs have served
  dog.not.served.counter<-0   # number of dogs have rejected
  cat.not.served.counter<-0   # number of cats have rejected
  dogs.times<-dogs.arrive.time  # arrival times vector of dogs
  cats.times<-cats.arrive.time   # arrival times vector of cats
  num_waited<-c(0)   # a vector of the number of queuing animals at all time intervals
  num_times<-c(0)   # a vector of the start time of the intervals 
  # as long as 12 hours have not passed
  while(work.clock<=720)   
  {
    #"x" is the next animal that arrived
    x<-min(dogs.times[1],cats.times[1])
    # check if "x" is a dog or a cat
    if(x==dogs.times[1])
    {
      type_x<-"dog" 
    }else
    {
      type_x<-"cat"
    }
    # if the shop is open
    if(work.clock<x)
    {
      # if there is no animal that in the queue
      if(length(waited)==0)
      {
        # so "x" can enter to the shop
        serve_start_time<-x
        # calculate the time that "x" will finish the service
        if(type_x=="dog")
        {
          work.clock<-serve_start_time+dogs.serve.time[which(dogs.arrive.time==x)]
        }
        if(type_x=="cat")
        {
          work.clock<-serve_start_time+cats.serve.time[which(cats.arrive.time==x)]
        }
        # check if "x" will finish the srvice before the shop will close
        if(work.clock<=720)
        {
          if(type_x=="dog")
          {
            dog.served.counter<-dog.served.counter+1
            profit<-profit+1
            dogs_out<-c(dogs_out,x)
            dogs.times<-dogs.times[-1]
          }
          if(type_x=="cat")
          {
            cat.served.counter<-cat.served.counter+1
            profit<-profit+3
            cats_out<-c(cats_out,x)
            cats.times<-cats.times[-1]
          }
        }
      }
      # if the shop is open now, but there are animals that waiting in the queue before "x"
      if(length(waited)>0)
      {
        # the first animals in the queue will enter to get a service
        serve_start_time<-work.clock
        num_times<-c(num_times, serve_start_time)
        # check if the first animal in the queue is a dog or a cat
        if(any(dogs_out==waited[1]))
        {
          first_waited_type<-"dog"
        }
        if(any(cats_out==waited[1]))
        {
          first_waited_type<-"cat"
        }
        # calculate the time that the first animal in the queue will finish the service
        if(first_waited_type=="dog")
        {
          work.clock<-serve_start_time+dogs.serve.time[which(dogs.arrive.time==waited[1])]
        }
        if(first_waited_type=="cat")
        {
          work.clock<-serve_start_time+cats.serve.time[which(cats.arrive.time==waited[1])]
        }
        # check if he will finish before the shop will close
        if(work.clock<=720)
        {
          if(first_waited_type=="dog")
          {
            dog.served.counter<-dog.served.counter+1
            profit<-profit+1
          }
          if(first_waited_type=="cat")
          {
            cat.served.counter<-cat.served.counter+1
            profit<-profit+3
          }
          #remove the customer from the queue
          waited<-waited[-1]
          num_waited<-c(num_waited, length(waited))
        }
      }
      # if the shop is not open  
    }else
    {
      #if "x" is a cat
      if(type_x=="cat")
      {
        # and there is nobody that waiting in queue ,
        #"x" will enter the queue
        if(length(waited)==0)
        {
          waited<-c(waited,x)
          num_waited<-c(num_waited, length(waited))
          num_times<-c(num_times, waited[length(waited)])
          #if there are customers that waiting in the queue,
          #"x" will be rejected
        }else
        {
          cat.not.served.counter<-cat.not.served.counter+1
        }
        cats_out<-c(cats_out,x)
        cats.times<-cats.times[-1]
      }
      #if "x" is a dog
      if(type_x=="dog")
      {
        #and there is a place for "x" in the queue, 
        #"x" will enter the queue
        if(length(waited)<20)
        {
          waited<-c(waited,x)
          num_waited<-c(num_waited, length(waited))
          num_times<-c(num_times, waited[length(waited)])
          #if there is no place for "x" in the queue
          #"x" will be rejected
        }else
        {
          dog.not.served.counter<-dog.not.served.counter+1
          profit<-profit-0.1
        }
        dogs_out<-c(dogs_out,x)
        dogs.times<-dogs.times[-1]
      }
    }
  }
  # calculate the average number of animals in the queue
  num_times_help<-(num_times)-(c(0,num_times[-length(num_times)]))
  final_num_times<-num_times_help[-1]
  if(length(num_waited)>length(final_num_times))
  {
    if(num_waited[length(num_waited)]==0)
    {
      num_waited<-num_waited[-length(num_waited)]
    }
  }
  mean_queue<-(sum(num_waited * final_num_times))/720
  return(list("dogs_served"=dog.served.counter, "dogs_reject"=dog.not.served.counter, "cats_served"=cat.served.counter, "cats_reject"=cat.not.served.counter, "profit"=profit, "mean_queue"=mean_queue))
}
```

```{r}
results_2_a<-replicate(100,dogcatia_20())

dogs_served_estimator_20 <- mean(as.numeric(results_2_a[1,]))
dogs_reject_estimator_20<-mean(as.numeric(results_2_a[2,]))
cats_served_estimator_20<-mean(as.numeric(results_2_a[3,]))
cats_reject_estimator_20<-mean(as.numeric(results_2_a[4,]))
profit_estimator_20<-mean(as.numeric(results_2_a[5,]))
mean_queue_estimator_20<-mean(as.numeric(results_2_a[6,])) 
```

```{r}
cat(paste("The dogs served estimator is",dogs_served_estimator_20,
        "The dogs reject estimator is",dogs_reject_estimator_20,
        "The cats served estimator is",cats_served_estimator_20,
        "The cats reject estimator is",cats_reject_estimator_20,
        "The profit estimator is",profit_estimator_20,
        "The mean queue estimator is",mean_queue_estimator_20,sep = "\n"))
```

Because the dogs arrive more often, they will "take over" the queue.
They are the ones who will get the most service so the main downside is that the company’s profit will go down.
The cats are the ones who will be harmed by this because the chance of the queue being empty is smaller in this situation.

### b ###


```{r}
dogcatia_service_rate_increased_by_10_precent<-function()
{
  # arrival times of dogs
  dogs.arrive.time<-rexp(1,3)
  
  while(dogs.arrive.time[length(dogs.arrive.time)]<720)
  {
    dogs.arrive.time<-c(dogs.arrive.time,dogs.arrive.time[length(dogs.arrive.time)]+rexp(1,3))
  }
  
  # arrival times of cats
  cats.arrive.time<-rexp(1,1.5)
  while(cats.arrive.time[length(cats.arrive.time)]<720)
  {
    cats.arrive.time<-c(cats.arrive.time,cats.arrive.time[length(cats.arrive.time)]+rexp(1,1.5))
  }
  
  #service time's of dogs
  dogs.serve.time<-rexp(length(dogs.arrive.time),3.3)
  
  #service time's of cats
  cats.serve.time<-rexp(length(cats.arrive.time),5.5)
  
  
  # initialization
  work.clock<-0   # marks the current time
  serve_start_time<-0   # a time when the next animal serve will begin
  profit<-0   # the company profit
  waited<-c()   # a vector of the queuing aninals
  dogs_out<-c()   # a vector for the served dogs
  cats_out<-c()   # a vector for the served cats
  dog.served.counter<-0   #number of dogs have served 
  cat.served.counter<-0   #number of dogs have served
  dog.not.served.counter<-0   # number of dogs have rejected
  cat.not.served.counter<-0   # number of cats have rejected
  dogs.times<-dogs.arrive.time  # arrival times vector of dogs
  cats.times<-cats.arrive.time   # arrival times vector of cats
  num_waited<-c(0)   # a vector of the number of queuing aninals at all time intervals
  num_times<-c(0)   # a vector of the start time of the intervals 
  # as long as 12 hours have not passed
  while(work.clock<=720)   
  {
    #"x" is the next animal that arrived
    x<-min(dogs.times[1],cats.times[1])
    # check if "x" is a dog or a cat
    if(x==dogs.times[1])
    {
      type_x<-"dog" 
    }else
    {
      type_x<-"cat"
    }
    # if the shop is open
    if(work.clock<x)
    {
      # if there is no animal that in the queue
      if(length(waited)==0)
      {
        # so "x" can enter to the shop
        serve_start_time<-x
        # calculate the time that "x" will finish the service
        if(type_x=="dog")
        {
          work.clock<-serve_start_time+dogs.serve.time[which(dogs.arrive.time==x)]
        }
        if(type_x=="cat")
        {
          work.clock<-serve_start_time+cats.serve.time[which(cats.arrive.time==x)]
        }
        # check if "x" will finish the srvice before the shop will close
        if(work.clock<=720)
        {
          if(type_x=="dog")
          {
            dog.served.counter<-dog.served.counter+1
            profit<-profit+1
            dogs_out<-c(dogs_out,x)
            dogs.times<-dogs.times[-1]
          }
          if(type_x=="cat")
          {
            cat.served.counter<-cat.served.counter+1
            profit<-profit+3
            cats_out<-c(cats_out,x)
            cats.times<-cats.times[-1]
          }
        }
      }
      # if the shop is open now, but there are animals that waiting in the queue before "x"
      if(length(waited)>0)
      {
        # the first animals in the queue will enter to get a service
        serve_start_time<-work.clock
        num_times<-c(num_times, serve_start_time)
        # check if the first animal in the queue is a dog or a cat
        if(any(dogs_out==waited[1]))
        {
          first_waited_type<-"dog"
        }
        if(any(cats_out==waited[1]))
        {
          first_waited_type<-"cat"
        }
        # calculate the time that the first animal in the queue will finish the service
        if(first_waited_type=="dog")
        {
          work.clock<-serve_start_time+dogs.serve.time[which(dogs.arrive.time==waited[1])]
        }
        if(first_waited_type=="cat")
        {
          work.clock<-serve_start_time+cats.serve.time[which(cats.arrive.time==waited[1])]
        }
        # check if he will finish before the shop will close
        if(work.clock<=720)
        {
          if(first_waited_type=="dog")
          {
            dog.served.counter<-dog.served.counter+1
            profit<-profit+1
          }
          if(first_waited_type=="cat")
          {
            cat.served.counter<-cat.served.counter+1
            profit<-profit+3
          }
          #remove the customer from the line
          waited<-waited[-1]
          num_waited<-c(num_waited, length(waited))
        }
      }
      # if the shop is not open  
    }else
    {
      #if "x" is a cat
      if(type_x=="cat")
      {
        # and there is nobody that waiting in queue ,
        #"x" will enter the queue
        if(length(waited)==0)
        {
          waited<-c(waited,x)
          num_waited<-c(num_waited, length(waited))
          num_times<-c(num_times, waited[length(waited)])
          #if there are customers that waiting in the queue,
          #"x" will be rejected
        }else
        {
          cat.not.served.counter<-cat.not.served.counter+1
        }
        cats_out<-c(cats_out,x)
        cats.times<-cats.times[-1]
      }
      #if "x" is a dog
      if(type_x=="dog")
      {
        #and there is a place for "x" in the queue, 
        #"x" will enter the queue
        if(length(waited)<10)
        {
          waited<-c(waited,x)
          num_waited<-c(num_waited, length(waited))
          num_times<-c(num_times, waited[length(waited)])
          #if there is no place for "x" in the queue
          #"x" will be rejected
        }else
        {
          dog.not.served.counter<-dog.not.served.counter+1
          profit<-profit-0.1
        }
        dogs_out<-c(dogs_out,x)
        dogs.times<-dogs.times[-1]
      }
    }
  }
  # calculate the average number of animals in the queue
  num_times_help<-(num_times)-(c(0,num_times[-length(num_times)]))
  final_num_times<-num_times_help[-1]
  if(length(num_waited)>length(final_num_times))
  {
    if(num_waited[length(num_waited)]==0)
    {
      num_waited<-num_waited[-length(num_waited)]
    }
  }
  mean_queue<-(sum(num_waited * final_num_times))/720
  return(list("dogs_served"=dog.served.counter, "dogs_reject"=dog.not.served.counter, "cats_served"=cat.served.counter, "cats_reject"=cat.not.served.counter, "profit"=profit, "mean_queue"=mean_queue))
}
```

```{r}
results_2_b<-replicate(100,dogcatia_service_rate_increased_by_10_precent())

dogs_served_estimator_service_rate_increased_by_10_precent <- mean(as.numeric(results_2_b[1,]))
dogs_reject_estimator_service_rate_increased_by_10_precent<-mean(as.numeric(results_2_b[2,]))
cats_served_estimator_service_rate_increased_by_10_precent<-mean(as.numeric(results_2_b[3,]))
cats_reject_estimator_service_rate_increased_by_10_precent<-mean(as.numeric(results_2_b[4,]))
profit_estimator_service_rate_increased_by_10_precent<-mean(as.numeric(results_2_b[5,]))
mean_queue_estimator_service_rate_increased_by_10_precent<-mean(as.numeric(results_2_b[6,])) 
```

```{r}
cat(paste("The dogs served estimator is",dogs_served_estimator_service_rate_increased_by_10_precent,
        "The dogs reject estimator is",dogs_reject_estimator_service_rate_increased_by_10_precent,
        "The cats served estimator is",cats_served_estimator_service_rate_increased_by_10_precent,
        "The cats reject estimator is",cats_reject_estimator_service_rate_increased_by_10_precent,
        "The profit estimator is",profit_estimator_service_rate_increased_by_10_precent,
        "The mean queue estimator is",mean_queue_estimator_service_rate_increased_by_10_precent,sep = "\n"))
```

### c ###

```{r}
dogcatia_queue_for_dogs_queue_for_cats<-function()
{
  # arrival times of dogs
  dogs.arrive.time<-rexp(1,3)
  
  while(dogs.arrive.time[length(dogs.arrive.time)]<720)
  {
    dogs.arrive.time<-c(dogs.arrive.time,dogs.arrive.time[length(dogs.arrive.time)]+rexp(1,3))
  }
  
  # arrival times of cats
  cats.arrive.time<-rexp(1,1.5)
  while(cats.arrive.time[length(cats.arrive.time)]<720)
  {
    cats.arrive.time<-c(cats.arrive.time,cats.arrive.time[length(cats.arrive.time)]+rexp(1,1.5))
  }
  
  #service time's of dogs
  dogs.serve.time<-rexp(length(dogs.arrive.time),3)
  
  #service time's of cats
  cats.serve.time<-rexp(length(cats.arrive.time),5)
  
  free_place.dogs<-0   # marks the current time for dogs
  place.dogs<-0   # a time when the next dog's service begins
  profit.dogs<-0   # the company profit from dogs 
  waited.dogs<-c()   # a vector of the queuing dogs
  free_place.cats<-0   # marks the current time for cats
  place.cats<-0   # a time when the next cat's service begins
  profit.cats<-0   #the company profit from cats 
  waited.cats<-c()   #a vector of the queuing cats
  dogs_out<-c()   # a vector for the served dogs
  cats_out<-c()   # a vector for the served cats
  dog.served.counter<-0   #number of dogs have served
  cat.served.counter<-0   #number of cats have served   
  dog.not.served.counter<-0   #number of dogs have rejected 
  cat.not.served.counter<-0   #number of cats have rejected 
  dogs.times<-dogs.arrive.time   # arrival times vector of dogs
  cats.times<-cats.arrive.time   # arrival times vector of cats
  num_waited.dogs<-c(0)   # a vector of the number of queuing dogs at all time intervals
  num_times.dogs<-c(0)   # a vector of the start time of the dogs intervals
  num_waited.cats<-c(0)   # a vector of the number of queuing cats at all time intervals
  num_times.cats<-c(0)   # a vector of the start time of the cats intervals
  #for dogs only
  while(free_place.dogs<=720)   #as long as 12 hours have not passed
  {
    #"x" is the next dog that arrived
    x<-dogs.times[1]   
    #if the turtle is available now
    if(free_place.dogs<x)   
    {
      # and there is no dog that waiting in the queue
      if(length(waited.dogs)==0)
      {
        #so "x" can go inside
        place.dogs<-x
        #calculate the time that "x" will finish the service
        free_place.dogs<-place.dogs + dogs.serve.time[which(dogs.arrive.time==x)]
        #check if "x" will finish before 12 hours have  passed
        if(free_place.dogs<=720)
        {
          dog.served.counter<-dog.served.counter+1
          profit.dogs<-profit.dogs+1
          dogs_out<-c(dogs_out,x)
          dogs.times<-dogs.times[-1]
        }
      }
      #if the turtle is available now, but there are dogs that waiting in the queue before "x"
      if(length(waited.dogs)>0)
      {
        #the first dog in the queue will enter 
        place.dogs<-free_place.dogs
        num_times.dogs<-c(num_times.dogs, place.dogs)
        #calculate the time that the first dog in the queue will finish the service
        free_place.dogs<-place.dogs+dogs.serve.time[which(dogs.arrive.time==waited.dogs[1])]
        #check if he will finish before the shop closed
        if(free_place.dogs<=720)
        {
          dog.served.counter<-dog.served.counter+1
          profit.dogs<-profit.dogs+1
          #remove the dog from the queue
          waited.dogs<-waited.dogs[-1]
          num_waited.dogs<-c(num_waited.dogs, length(waited.dogs))
        }
      }
      #if the turtle is not available now
    }else
    {
      #if there is a place for "x" in the queue, 
      #"x" will enter the queue
      if(length(waited.dogs)<9)
      {
        waited.dogs<-c(waited.dogs,x)
        num_waited.dogs<-c(num_waited.dogs, length(waited.dogs))
        num_times.dogs<-c(num_times.dogs, waited.dogs[length(waited.dogs)])
        #if there is no place for "x" in the queue, 
        #"x" will be rejected
      }else
      {
        dog.not.served.counter<-dog.not.served.counter+1
        profit.dogs<-profit.dogs-0.1
      }
      dogs_out<-c(dogs_out,x)
      dogs.times<-dogs.times[-1]
    }
  }
  #calculate the average number of dogs in the queue
  num_times_help.dogs<-(num_times.dogs)-(c(0,num_times.dogs[-length(num_times.dogs)]))
  final_num_times.dogs<-num_times_help.dogs[-1]
  if(length(num_waited.dogs)>length(final_num_times.dogs))
  {
    if(num_waited.dogs[length(num_waited.dogs)]==0)
    {
      num_waited.dogs<-num_waited.dogs[-length(num_waited.dogs)]
    }
  }
  mean_queue.dogs<-(sum(num_waited.dogs * final_num_times.dogs))/720
  #for cats only
  while(free_place.cats<=720)   #as long as 12 hours have not passed
  {
    #"y" is the next cat that arrived
    y<-cats.times[1]
    #if the turtle is available now
    if(free_place.cats<y)
    {
      #and there is no cat that waiting in the queue
      if(length(waited.cats)==0)
      {
        #so "y" can go inside
        place.cats<-y
        #calculate the time that "y" will finish the service
        free_place.cats<-place.cats+cats.serve.time[which(cats.arrive.time==y)]
        #check if "y" will finish before 12 hours have  passed
        if(free_place.cats<=720)
        {
          cat.served.counter<-cat.served.counter+1
          profit.cats<-profit.cats+3
          cats_out<-c(cats_out,y)
          cats.times<-cats.times[-1]
        }
      }
      #if the turtle is available now, but there is a cat that waiting in the queue before "y"
      if(length(waited.cats)==1)
      {
        #the cat in the queue will enter
        place.cats<-free_place.cats
        num_times.cats<-c(num_times.cats, place.cats)
        #calculate the time that the cat in the queue will finish the service
        free_place.cats<-place.cats+cats.serve.time[which(cats.arrive.time==waited.cats)]
        #check if he will finish before the shop closed
        if(free_place.cats<=720)
        {
          cat.served.counter<-cat.served.counter+1
          profit.cats<-profit.cats+3
          #remove the cat from the queue
          waited.cats<-waited.cats[-1]
          num_waited.cats<-c(num_waited.cats, length(waited.cats))
        }
      }
      #if the turtle is not available now
    }else
    {
      #if there is no cat that waiting in the queue, 
      #"y" will enter the queue
      if(length(waited.cats)==0)
      {
        waited.cats<-c(waited.cats,y)
        num_waited.cats<-c(num_waited.cats, length(waited.cats))
        num_times.cats<-c(num_times.cats, waited.cats[length(waited.cats)])
        #if there is a cat that waiting in the queue, 
        #"y" will be rejected      
      }else
      {
        cat.not.served.counter<-cat.not.served.counter+1
      }
      cats_out<-c(cats_out,y)
      cats.times<-cats.times[-1]
    }
  }
  #calculate the average number of cats in the queue
  num_times_help.cats<-(num_times.cats)-(c(0,num_times.cats[-length(num_times.cats)]))
  final_num_times.cats<-num_times_help.cats[-1]
  if(length(num_waited.cats)>length(final_num_times.cats))
  {
    if(num_waited.cats[length(num_waited.cats)]==0)
    {
      num_waited.cats<-num_waited.cats[-length(num_waited.cats)]
    }
  }
  mean_queue.cats<-(sum(num_waited.cats * final_num_times.cats))/720
  #calculate the total profit of the company
  total_profit<-profit.cats+profit.dogs
  return(list("dogs_served"=dog.served.counter, "dogs_reject"=dog.not.served.counter, "cats_served"=cat.served.counter, "cats_reject"=cat.not.served.counter, "profit"=total_profit, "mean_queue_dogs"=mean_queue.dogs, "mean_queue_cats"=mean_queue.cats))
}
```


```{r}
results_2_c<-replicate(100,dogcatia_queue_for_dogs_queue_for_cats())

dogs_served_estimator_queue_for_dogs_queue_for_cats <- mean(as.numeric(results_2_c[1,]))
dogs_reject_estimator_queue_for_dogs_queue_for_cats<-mean(as.numeric(results_2_c[2,]))
cats_served_estimator_queue_for_dogs_queue_for_cats<-mean(as.numeric(results_2_c[3,]))
cats_reject_estimator_queue_for_dogs_queue_for_cats<-mean(as.numeric(results_2_c[4,]))
profit_estimator_queue_for_dogs_queue_for_cats<-mean(as.numeric(results_2_c[5,]))
mean_queue_dods_estimator_queue_for_dogs_queue_for_cats<-mean(as.numeric(results_2_c[6,]))
mean_queue_cats_estimator_queue_for_dogs_queue_for_cats<-mean(as.numeric(results_2_c[7,]))
```


```{r}
cat(paste("The dogs served estimator is",dogs_served_estimator_queue_for_dogs_queue_for_cats,
        "The dogs reject estimator is",dogs_reject_estimator_queue_for_dogs_queue_for_cats,
        "The cats served estimator is",cats_served_estimator_queue_for_dogs_queue_for_cats,
        "The cats reject estimator is",cats_reject_estimator_queue_for_dogs_queue_for_cats,
        "The profit estimator is",profit_estimator_queue_for_dogs_queue_for_cats,
        "The mean dogs queue estimator is",mean_queue_dods_estimator_queue_for_dogs_queue_for_cats,
        "The mean cats queue estimator is",mean_queue_cats_estimator_queue_for_dogs_queue_for_cats,sep = "\n"))
```

We recommend the third option because the amount of dogs and cats (together) that receive service is the highest.
In addition the company's profit from this option is the highest

